(Animal) Life-Cycle Algorithm\thanks{Supported by organization x.}

### 2021-07-09 paper.tex
Bibliography
Bib external file
Update paper.tex

\begin{document}
%
\title{(Animal) Life-Cycle Algorithm\thanks{Supported by organization x.}}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{First Author\inst{1}\orcidID{0000-1111-2222-3333} \and
Second Author\inst{2,3}\orcidID{1111-2222-3333-4444} \and
Third Author\inst{3}\orcidID{2222--3333-4444-5555}}
%
\authorrunning{F. Author et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Princeton University, Princeton NJ 08544, USA \and
Springer Heidelberg, Tiergartenstr. 17, 69121 Heidelberg, Germany
\email{lncs@springer.com}\\
\url{http://www.springer.com/gp/computer-science/lncs} \and
ABC Institute, Rupert-Karls-University Heidelberg, Heidelberg, Germany\\
\email{\{abc,lncs\}@uni-heidelberg.de}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
%The abstract should briefly summarize the contents of the paper in 150--250 words.
This paper is a proposal for a nature-inspired algorithm that seeks to solve the basic GA problem OneMax. This is a distributed algorithm in all its conception, where the idea is that its mechanism can operate from different containers (or equipment) independently, eliminating waiting times between processes. This algorithm emphasizes the use of cloud computing available resources.

@@

This implementation also can be useful, as an introductory example to the native cloud computing programming, inspired by the GA algorithm operation mechanics. One difference from the GA is in the reproduction mechanism, which is flexible to work in parallel with several strategies simultaneously, for example, tourney selection, random selection of couples in the population, and couple selection with a random mating individual outside of the population.
\keywords{First keyword  \and Second keyword \and Another keyword.}
\end{abstract}
%
%
%
\section{First Section}
\subsection{A Subsection Sample}
Please note that the first paragraph of a section or subsection is
not indented. The first paragraph that follows a table, figure,
equation etc. does not need an indent, either.

>>>>

\begin{document}
%
\title{(Animal) Life-Cycle Algorithm\thanks{Supported by organization x.}}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{First Author\inst{1}\orcidID{0000-1111-2222-3333} \and
Second Author\inst{2,3}\orcidID{1111-2222-3333-4444} \and
Third Author\inst{3}\orcidID{2222--3333-4444-5555}}
%
\authorrunning{F. Author et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Princeton University, Princeton NJ 08544, USA \and
Springer Heidelberg, Tiergartenstr. 17, 69121 Heidelberg, Germany
\email{lncs@springer.com}\\
\url{http://www.springer.com/gp/computer-science/lncs} \and
ABC Institute, Rupert-Karls-University Heidelberg, Heidelberg, Germany\\
\email{\{abc,lncs\}@uni-heidelberg.de}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
%The abstract should briefly summarize the contents of the paper in 150--250 words.
There are several bio-inspired algorithms that are use analogies of na

This paper is a proposal for a novel nature-inspired algorithm that seeks to solve the
basic GA problem OneMax. This is a distributed algorithm in all its conception,

% In this paper, we present a novel distributed nature-inspired algorithm, for solving 
% optimization problems.

% Considera la opción de arriba para el inicio, creo que es más concisa. 
% El algoritmo es para problemas de optimización en general, no solo OneMax 
% - Mario

where the idea is that its mechanism can operate from different containers (or
equipment) independently, eliminating waiting times between processes. This
algorithm emphasizes the use of cloud computing available resources.

% Algo como: from the ground up, the algorithm is designed as a cloud-native
%

% The algorithm in inspired in the biologycal life-cycle of animal species, which consists
% of several phases  birth, growth, reproduction, and death. 
% As in nature, we intend to execute all these "phases" in parallel and asynchronously

@@

% As a proof-of-concept we implemented the algorithm  ... 
% by using the OneMax problem  
%

This implementation also can be useful, as an introductory example to the native
cloud computing programming, inspired by the GA algorithm operation mechanics.
One difference from the GA is in the reproduction mechanism, which is flexible
to work in parallel with several strategies simultaneously, for example, tournament 
selection, random selection of couples in the population, and couple selection
with a random mating individual outside of the population.

\keywords{First keyword  \and Second keyword \and Another keyword.}
\end{abstract}
%
%
%
\section{First Section}
\subsection{A Subsection Sample}
Please note that the first paragraph of a section or subsection is
not indented. The first paragraph that follows a table, figure,
equation etc. does not need an indent, either.
